Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-08-04 doc/ms.tex
Update manuscript to reflect RATIR observations

Photometric observations in the \textit{BVg'r'i'} filters were conducted by the Las Cambres Observatory (LCO) 1-m
telescope network.  PSF photometry was measured on these images using
the \texttt{lcogtsnpipe} pipeline \citep{2016MNRAS.459.3939V}. The
\textit{BV} magnitudes are calibrated to the Fourth USNO CCD
Astrograph Catalog \citep{2013AJ....145...44Z}, and the \textit{g'r'i'}
magnitudes are calibrated to SDSS Data Release 6
\citep{2008ApJS..175..297A}.

@@

The $g$-band discovery data and color curves of \abc\ are 
illustrated in Figure~\ref{fig:lightcurve}.  For convenience, 
magnitudes in 
\textit{all} filters are in the AB system with a zero point of 
$3631$\,Jy. As previously noted the color terms necessary to convert the $g_\mathrm{PTF}$ and $R_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.

>>>>

Photometric observations in the $BVg'r'i'$ filters were conducted by the Las Cambres Observatory (LCO) 1-m
telescope network.  PSF photometry was measured on these images using
the \texttt{lcogtsnpipe} pipeline \citep{2016MNRAS.459.3939V}. The
\textit{BV} magnitudes are calibrated to the Fourth USNO CCD
Astrograph Catalog \citep{2013AJ....145...44Z}, and the \textit{g'r'i'}
magnitudes are calibrated to SDSS Data Release 6
\citep{2008ApJS..175..297A}.

The Reionization and Transients InfraRed (RATIR) camera on the autonomous 1.5\,m Harold L. Johnson Telescope at the Observatorio Astron\'{o}mico Nacional \citep{2012SPIE.8446E..10B} was used to observe \abc\ in the $r'i'ZYJH$ filters. The $r'i'Z$ filters are calibrated to SDSS, while the $JH$ filters are calibrated to the Two Micron All Sky Survey \citep{2006AJ....131.1163S}. For the $Y$-band calibration, we used an empirical relation in terms of the $J$ and $H$ magnitudes derived from the United Kingdom Infrared Telescope (UKIRT; \citealt{2007A&A...467..777C}) Wide Field Camera observations \citep{2009MNRAS.394..675H}.

@@

The $g$-band discovery and follow-up data of \abc\ are 
illustrated in Figure~\ref{fig:lightcurve}.  The photometry is shown in the AB system with a zero point of 
$3631$\,Jy. As previously noted the color terms necessary to convert $g_\mathrm{PTF}$ to the AB system are unknown and assumed to be zero.
